The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-27 sandbox/note_km.tex
update KM note

Using this distance, the number of searchable stars $N\s$ is given by
\begin{equation}
	N\s(\delta_{\rm obs}, L_{\rm sys})=n_0 \delta_{\rm obs}^3 L_{\rm 
	sys}^{3/2},
\end{equation}
where $n_0$ is a normalization constant proportional to the volume density of the systems with a certain type of interest (e.g. single star, binary).
We neglect the dependence of the normalization $n_0$ on the stellar type.

@@

We assume that the apparent property of an unresolved binary is the same as that of the primary:
\begin{equation}
	M\a=M_1, \quad R\a=R_1, ...
\end{equation}
We also assume the stellar radius and luminosity is uniquely related to the stellar mass.

Given these assumptions, the total luminosity of the system is
%This assumption, along with a given $L$--$M$ relation, leads to
\begin{equation}
	L_{\rm sys}=L_1+L_2=L(M\a)+L(qM\a),
\end{equation}
where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
the true primary mass), while the system luminosity estimated by an observer 
would be $L(M\a)$, which based on the apparent stellar parameters (unless the 
observer has a priori knowledge on the distance to a given system).

@@

Given the apparent signal $\delta_{\rm obs}$ and stellar mass $M\a$, the 
maximum searchable distance for singles and binaries are proportional to 
$\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot 
[L(M\a)+L(qM\a)]^{1/2}$. Thus, 
the apparent number of searchable stars (i.e. points in the sky), which will 
be selected by an ignorant observer, is 
\begin{align}
	\notag
	N_{\rm s,a}(\delta_{\rm obs}, M\a)
	%&=n_{\rm s,0}\delta_{\rm obs}^3L(M\a)^{3/2} + n_{\rm b,0}\delta_{\rm 
	%obs}^3 \cdot [L(M\a)+L(qM\a)]^{3/2}\\
	&=n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left\{1+\int \mathrm{d}q\,f(q) 
	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
	L(M\a)}\right]^{3/2}\right\}\\
	&\equiv N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
	M\a)\right],
\end{align}
where $N\s^0$ is the number of searchable singles (this agrees with the actual value), $f(q)$ is the binary mass ratio distribution, and $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ is the binary fraction in a volume-limited sample.

@@

A group of astronomers wants to measure the mean number of planets of a 
certain type per star of a certain type.
They simply observe a set points on the sky selected in a magnitude-limited way (or whatever, actually?) and detect $n$ planets of a desired class. Then they compute the occurrence as
\begin{equation}
\Lambda(\pp, \ps) = \frac{n(\pp, \ps)}{N_{\rm s}(\pp, \ps)} \times \frac{1}{p_{\rm tra}(\pp, \ps)}.
\end{equation}
Here $N_{\rm s}$ is the number of stars (among those initially selected) around which the planets of interest are searchable; $p_{\rm tra}$ is the transit probability.

Let's see how the binary modifies this. The occurrence is computed based on the apparent planetary/stellar parameters $\pp\a$, $\ps\a$:
\begin{equation}
\Lambda\a(\pp\a, \ps\a) = \frac{n(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
\end{equation}
Here, $N_{\rm s}$ and $p_{\rm tra}$ are computed for the apparent parameter $\pp\a$ and $\ps\a$. In the presence of dilution, planets with $(\pp\a, \ps\a)$ are associated with systems of many different planetary and stellar properties, so $n_{\rm a}$ is given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and number of searchable stars that give $(\pp\a, \ps\a)$ when the true system actually has $(\pp, \ps)$, $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$:
\begin{equation}
	n(\pp\a, \ps\a)=\sum_i n^i(\pp\a, \ps\a)
	=\sum_i \int \mathrm{d}\pp\mathrm{d}\ps\,
	%\mathcal{P}_{\rm tra}(\pp\a, \ps\a; \pt)
	\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
	\cdot\Lambda^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
\end{equation}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: secondary).
%where $b_i=1-\mathrm{BF}$ for $i=0$ (singles) and $b_i=\mathrm{BF}$ for $i=1,2$. In fact, the $b_i$ factor appears when we count the number of searchable systems $\mathcal{N}$; what matters here is the number density of binaries and singles, so $\mathrm{BF}$ is the binary fraction in a volume-limited sample. Here we factor it out just to simplify(?) the notation.

So the problem essentially reduces to the evaluation of
\begin{equation}
	\mathcal{N}_{\rm s}(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in binaries.

\section{Evaluation of $\mathcal{N}$}

Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely determined from the assumed mass--radius--luminosity relation. We neglect the $P$ dependence.

@@

For $i=0$, 
\begin{equation}
	\mathcal{N}_{\rm s}^0(\pp\a,\ps\a; \pp, \ps)
	=\delta(\pp\a-\pp)\delta(\ps\a-\ps) N\s^0(\pp,\ps),
	%=\delta(r'-r)\delta(M'-M)\delta(R'-R) N\s((r/R)^2, L(M))
\end{equation}
so
\begin{equation}
	n^0(\pp\a, \ps\a)=N\s^0(\pp\a,\ps\a)\cdot \Lambda^0(\pp\a, \ps\a) \cdot p_{\rm tra}(\pp\a, \ps\a).
\end{equation}
If all the stars are singles, this yields
\begin{equation}
	\Lambda\a(\pp\a, \ps\a)=\Lambda^0(\pp\a, \ps\a),
\end{equation}
as expected (now $\mu=0$ and $N_{\rm s,a}=N\s^0$) --- the true occurrence is recovered.

@@

Since we assume $\ps\a=\ps_1$,
\begin{equation}
	\mathcal{N}_{\rm s}^1(r', M'; r, M) \propto \delta(M'-M).
	%=\mathcal{N}_{\rm s}^1(r', M', R'; r, M', R').
\end{equation}
In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at $r'=R'\sqrt{D'}$, where
\begin{equation}
	D' %= \delta \times {L_1 \over L_{\rm sys}} 
	= \left[{r\over R(M')}\right]^2\times {L(M') \over L_{\rm sys}(M', q)}
\end{equation}
and the normalization is given by the number of searchable binaries (for signal $D'$):
\begin{equation}
	%N_{\rm s}(D', L_{\rm sys})
	n_{\rm b}D'^3 L_{\rm sys}^{3/2}=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M').
	%=N_{\rm s}(D', L(M')) \times \left[L_{\rm sys}(M', q) \over L(M') 
	%\right]^{3/2}.
\end{equation}
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^1(r', M'; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r', M'; r, M; q),
\end{equation}
where $f(q)$ is the binary mass ratio distribution and
\begin{align}
	\notag
	\mathcal{N}_{{\rm s}, q}^1(r', M'; r, M; q)
	%&=N_{\rm s}(D', L(M')) \left[L_{\rm sys}(M', q) \over L(M') 
	%\right]^{3/2}\\
	&=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M')\\
	&\times\delta \left(r'-r\sqrt{{L(M') \over L_{\rm sys}(M', 
	q)}}\right)\delta(M'-M).
\end{align}

@@

In this case, $M=qM_1=qM'$, so
\begin{equation}
	\mathcal{N}_{\rm s}^2(r', M'; r, M)
	\propto \delta\left(M'-{M\over q}\right).
	%=\mathcal{N}_{\rm s}^2(r', M', R'; r, qM', R(qM')).
\end{equation}
Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r'=R'\sqrt{D'}$, but this time
\begin{equation}
	D' = \left[{r\over R(qM')}\right]^2 \times {L(qM') 
	\over L_{\rm sys}(M', q)}.
\end{equation}
The normalization remains the same as the previous case (we are counting the searchable stars at a given observed depth $D'$, total luminosity of the binary is the same).
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^2(r', M'; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r', M'; r, M; q),
\end{equation}
where
\begin{align}
	\notag
	\mathcal{N}_{\rm s}^2(r', M'; r, M; q)
	%&=N_{\rm s}(D', L(M')) \left[L_{\rm sys}(M', q) \over L(M') 
	%\right]^{3/2}\\
	&=N_{\rm s}^0(D', L(M'))\cdot\mu(\mathrm{BF},M')\\
	&\times \delta \left(r'-r\sqrt{ \left[{R(M')\over R(qM')}\right]^2 {L(qM') 
	\over L_{\rm sys}(M', q)} }\right)\delta\left(M'-{M\over q}\right).
\end{align}

@@

\begin{align}
	n^0(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
	&=\int\mathrm{d}r\mathrm{d}M\, N\s^0(\delta_{\rm obs}, 
	L(M\a))\delta(r\a-r)\delta(M\a-M)
	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Lambda^0(r\a, M\a) \cdot p_{\rm 
	tra}(M\a).
\end{align}

\begin{align}
	n^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a; r, M; q)\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1(r^*, M\a),
	%\left[L_{\rm sys}(M', q) \over L(M') \right]^{3/2},
\end{align}
where $r^*=r\a/\alpha$ and 
\begin{equation}
	\alpha(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	n^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)\\
	&=%N_{\rm s}(D', L(M')
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r^{**}, qM\a)\,p_{\rm tra}(qM\a),
	%\left[L_{\rm sys}(M', q) \over L(M') \right]^{3/2},
\end{align}
where $r^{**}=r\a/\beta$ and 
\begin{equation}
	\beta(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }.
\end{equation}

@@

Note again that the denominators of $\Lambda\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent occurrence is thus given by
\begin{align}
	&\Lambda\a(r\a, M\a)={1\over 1+\mu(\mathrm{BF}, M\a)}\times\\
	%&=(1-\mathrm{BF})\cdot
	&\left\{ \Lambda^0(r\a, M\a)+ \mu(\mathrm{BF}, M\a) \left[
	\int {\mathrm{d}q \over A}\,f(q)\,\Lambda^1\left({r\a\over A}, M\a\right)\,
	+\int {q \mathrm{d}q \over B}\,f(q)\,\Lambda^2\left({r\a\over B}, qM\a\right)\,
	{R(qM\a) \over R(M\a)}
	q^{-1/3} \right]
	\right\},
	 %\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2}
	 %\\
	%&+\mathrm{BF}\cdot
	%\int {q \mathrm{d}q \over B}\,f(q)\,\Lambda^2\left({r\a\over B}, qM\a\right)\,
	%{R(qM\a) \over R(M\a)}q^{-1/3}
	%\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2},
\end{align}
where
\begin{equation}
	A=\left[1+{L(qM\a) \over L(M\a)}\right]^{-1/2}, \quad
	B={R(M\a)\over R(qM\a)}\left[1+{L(M\a) \over L(qM\a)}\right]^{-1/2}.
\end{equation}

>>>>

Assuming that stars are uniformly distributed in space, the number of 
searchable stars $N\s$ is then proportional to
\begin{equation}
	N\s(\delta_{\rm obs}, L_{\rm sys}) \propto n \delta_{\rm obs}^3 L_{\rm 
	sys}^{3/2},
\end{equation}
where $n$ is the volume density of {\it e.g.}, single star, or binary systems.
We neglect the dependence of $n$ on stellar type.

@@

We assume that the apparent properties of an unresolved binary are the same as 
those of the primary:
\begin{equation}
	M\a=M_1, \quad R\a=R_1, ...
\end{equation}
We also assume the stellar radius and luminosity is uniquely related to the 
stellar mass.

Given these assumptions, the total luminosity of a system is
\begin{equation}
	L_{\rm sys}=L_1+L_2=L(M\a)+L(qM\a),
\end{equation}
where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
the true primary mass), while an observer would estimate a system luminosity 
of $L(M\a)$, based on the apparent stellar parameters. We presume the 
observer has no a priori knowledge of the distance to a given system~--~they 
only measure a flux, assume a stellar mass $M_a$, and use relations for 
$L(M_a)$ and $R(M_a)$ to estimate system properties.

@@

Given the apparent signal $\delta_{\rm obs}$ and stellar mass $M\a$, the 
maximum searchable distance for singles and binaries are proportional to 
$\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot 
[L(M\a)+L(qM\a)]^{1/2}$. Thus, 
the apparent number of searchable stars (i.e. points in the sky), which will 
be selected by an ignorant observer, can be written 
\begin{align}
	\notag
	N_{\rm s,a}(\delta_{\rm obs}, M\a)
	%&=n_{\rm s,0}\delta_{\rm obs}^3L(M\a)^{3/2} + n_{\rm b,0}\delta_{\rm 
	%obs}^3 \cdot [L(M\a)+L(qM\a)]^{3/2}\\
	&\propto n_{\rm s}\delta_{\rm obs}^3 L(M\a)^{3/2}\left[ 1+\int 
	\mathrm{d}q\,f(q) 
	{\mathrm{BF}\over{1-\mathrm{BF}}}\left(1+{L(qM\a) \over 
	L(M\a)}\right)^{3/2}\right]\\
	N_{\rm s,a}(\delta_{\rm obs}, M\a)
    &\equiv N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
	M\a)\right],
\end{align}
where $N\s^0$ is the number of searchable singles (this agrees with the actual 
value), $f(q)$ is the binary mass ratio distribution, $\mathrm{BF}=n_{\rm 
b}/(n_{\rm s}+n_{\rm b})$ is the binary fraction in a volume-limited sample, 
and $n_s$ is the number density of singles in a volume-limited sample.
Proportionality constants subsumed into the definition of $N_s^0$ include 
{\it e.g.}, the telescope area and the survey duration.

@@

A group of astronomers wants to measure the mean number of planets of a 
certain type per star of a certain type.
They observe a set points on the sky and detect $N_{\rm det}$ planets that 
appear to be of the desired class.
They then choose the stars (among those initially selected) around which the 
planets of interest appeared to be searchable.
Finally they compute the apparent occurrence,
\begin{equation}
\Lambda\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
\end{equation}
where $\pp\a$, $\ps\a$ are the apparent planetary/stellar parameters.

In the presence of dilution, planets with $(\pp\a, \ps\a)$ are associated with 
systems of many different planetary and stellar properties, so $N_{\rm 
det}(\pp\a, \ps\a)$ is 
given by the convolution of the true occurrence, $\Lambda(\pp, \ps)$, and 
number of searchable stars that give $(\pp\a, \ps\a)$ when the true system 
actually has $(\pp, \ps)$, $\mathcal{N}(\pp\a, \ps\a; \pp, \ps)$:
\begin{equation}
	N_{\rm det}(\pp\a, \ps\a)=\sum_i N_{\rm det}^i(\pp\a, \ps\a)
	=\sum_i \int \mathrm{d}\pp\mathrm{d}\ps\,
	%\mathcal{P}_{\rm tra}(\pp\a, \ps\a; \pt)
	\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
	\cdot\Lambda^i(\pp, \ps)\cdot p_{\rm tra}(\pp, \ps),
\end{equation}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
secondary).

So the problem reduces to the evaluation of
\begin{equation}
	\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in binaries.

\section{Evaluation of 
    $\mathcal{N}_{\rm \MakeLowercase{s}}^{\MakeLowercase{i}}$}

Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
determined from the assumed mass--radius--luminosity relation. We neglect the 
dependence on planetary orbital period.
We proceed by evaluating
\begin{align}
N_{\rm det}(r_a, M_a) &=
\sum_i N_{\rm det}^i(r_a, M_a) \\
N_{\rm det}(r_a, M_a)
&=
\sum_i \int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
\cdot\Lambda^i(r,M) \cdot p_{\rm tra}(r,M),
\end{align}
term by term.

@@

For $i=0$, 
\begin{equation}
	\mathcal{N}_{\rm s}^0(r\a,M\a; r,M)
	=\delta(r\a-r)\delta(M\a-M) N\s^0(r,M),
\end{equation}
so
\begin{equation}
	N_{\rm det}^0(r\a, M\a)=N\s^0(r\a,M\a)\cdot \Lambda^0(r\a, 
	M\a) \cdot p_{\rm tra}(r\a, M\a).
\end{equation}
If all the stars are singles, this yields
\begin{equation}
	\Lambda\a(r\a, M\a)=\Lambda^0(r\a, M\a),
\end{equation}
as expected (now $\mu=0$ and $N_{\rm s,a}=N\s^0$) --- the true occurrence is 
recovered.

%TODO: PROCEED FROM HERE

@@

Since we assume $\ps\a=\ps_1$,
\begin{equation}
	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M) \propto \delta(M_a-M).
\end{equation}
In this case, $\mathcal{N}_{\rm s}^1$ is non-zero only at 
$r_a=R_a\sqrt{\delta_{\rm obs}}$, 
and the observed depth is
\begin{equation}
	\delta_{\rm obs}
	= \left[{r\over R(M_a)}\right]^2\times {L(M_a) \over L_{\rm sys}(M_a, q)}.
   \label{eq:delta_obs_primaries} 
\end{equation}
The normalization of $\mathcal{N}_{\rm s}^1$ is given by the number of 
binaries that are searchable for a signal $\delta_{\rm obs}$:
\begin{equation}
	N_{\rm s}^0(\delta_{\rm obs}, 
	L(M_a))\cdot\mu(\mathrm{BF},M_a).
\end{equation}
Thus, the number of primaries with apparent parameters $(r_a,M_a)$ given the 
true parameters $(r,M)$ is
\begin{equation}
	\mathcal{N}_{\rm s}^1(r_a, M_a; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q),
\end{equation}
where $f(q)$ is the binary mass ratio distribution and
\begin{align}
	\notag
	\mathcal{N}_{{\rm s}, q}^1(r_a, M_a; r, M; q)
	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
	&\times\delta \left(r_a-r\sqrt{{L(M_a) \over L_{\rm sys}(M_a, 
	q)}}\right)\delta(M_a-M).
\label{eq:N_s_1}
\end{align}
Note that while the observed depth is a function of the true parameters 
(Eq.~\ref{eq:delta_obs_primaries}), since we are counting 
detected planets of a given {\it apparent} size, we will not need to worry 
about this dependence.

@@

In this case, $M=qM_1=qM_a$, so
\begin{equation}
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
	\propto \delta\left(M_a-{M\over q}\right).
	%=\mathcal{N}_{\rm s}^2(r_a, M_a, R_a; r, qM_a, R(qM_a)).
\end{equation}
Again $\mathcal{N}_{\rm s}^2$ is non-zero only at $r_a=R_a\sqrt{\delta_{\rm 
obs}}$, but this 
time
\begin{equation}
	\delta_{\rm obs} = \left[{r\over R(qM_a)}\right]^2 \times {L(qM_a) 
	\over L_{\rm sys}(M_a, q)}.
\end{equation}
The normalization remains the same as the previous case (we are counting the 
searchable stars at a given observed depth $\delta_{\rm obs}$, total 
luminosity of the binary is the same).
Thus,
\begin{equation}
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M)
	=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r_a, M_a; r, M; q),
\end{equation}
where
\begin{align}
	\notag
	\mathcal{N}_{\rm s}^2(r_a, M_a; r, M; q)
	%&=N_{\rm s}(\delta_{\rm obs}, L(M_a)) \left[L_{\rm sys}(M_a, q) \over 
	%L(M_a) 
	%\right]^{3/2}\\
	&=N_{\rm s}^0(\delta_{\rm obs}, L(M_a))\cdot\mu(\mathrm{BF},M_a)\\
	&\times \delta \left(r_a-r\sqrt{ \left[{R(M_a)\over R(qM_a)}\right]^2 
	{L(qM_a) 
	\over L_{\rm sys}(M_a, q)} }\right)\delta\left(M_a-{M\over q}\right).
\end{align}

@@

\begin{align}
	N_{\rm det}^0(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^0(r\a, M\a; r, M)
	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
	&=\int\mathrm{d}r\mathrm{d}M\, N\s^0(\delta_{\rm obs}, 
	L(M\a))\delta(r\a-r)\delta(M\a-M)
	\cdot\Lambda^0(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot\Lambda^0(r\a, M\a) \cdot p_{\rm 
	tra}(M\a).
\end{align}

\begin{align}
	N_{\rm det}^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a; r, M; q)\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
	\alpha}\,f(q)\,\Lambda^1(r_a/\alpha, M\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\alpha(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	N_{\rm det}^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
    \\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
    \\
    &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\beta) \Lambda^2(r,qM\a) 
    p_{\rm tra}(qM\a) \\
	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r_a/\beta, qM\a)\,p_{\rm 
	tra}(qM\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\beta(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }.
\end{equation}

@@

Note again that the denominators of $\Lambda\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent occurrence,
\begin{align}
\Lambda\a(r\a,M\a) &= 
    \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
    \sum_i N_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to
\begin{align}
\notag
\Lambda\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
   \left\{ \Lambda^0(r\a, M\a)+ 
\mu(\mathrm{BF}, M\a)
\left[ \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1\left({r\a\over 
    \alpha}, 
M\a\right)\,
\right.   
   \right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2\left({r\a\over \beta}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.  
\end{align}
